\documentclass[full]{rvca}

% Compile with XeLatex

\begin{document}

% % % % % % % % % % % Begin Side Panel

\begin{aside} % each new line forces a line break
\section{\uppercase{contact} }
407-1028 Alberni St.
Vancouver, BC.
V6E1A3. Canada.
+1 (778) 996 7359
\ghost
roberto@
\href{http://calderonroberto.com}{\color{sidebandtextcolor}calderonroberto.com \faGlobe}
\href{http://twitter.com/calderonroberto}{\color{sidebandtextcolor}@calderonroberto \faTwitter} 
\href{https://github.com/calderonroberto}{\color{sidebandtextcolor}@calderonroberto \faGithub} 
\href{https://ca.linkedin.com/in/calderonrobertocom}{\color{sidebandtextcolor}calderonrobertocom \faLinkedin} 
\ghost
% \QrCode
\ghost
\section{\uppercase{in a nutshell}}
Open-Minded\\Quick-learner\\Determined\\Explorer\\Creator 
% 
\ghost
\section{\uppercase{interests}}
SaaS, IoT, UI/UX, HCI, Startups, Innovation.
%
\ghost
\section{\uppercase{skills}}
Full-stack Web, UI/UX, 
HCI, Research, Writing.
\ghost 
\section{\uppercase{human code}}
English, Spanish, French
\ghost
\section{\uppercase{computer code}}
HTML5, CSS3, SASS \& LESS, {\scriptsize\faHeart} Javascript,
Angular \& React, RSpec, Mocha, Selenium, Grunt,
{\scriptsize\faHeart} RoR, {\scriptsize\faHeart} NodeJS, LAMP,
Ruby, Python, {\scriptsize\faHeart} Go,
MySQL, MongoDB, Redis,
Java, C++, {\scriptsize\faHeart} Linux
\end{aside}


\header{roberto}{calderon}{ } % Your name and current job title/field



% % % % % % % % % % Begin Main Content

\begin{statement}
Self motivated software developer, designer and entrepreneur with over 5 years of experience working with innovation and research in web technologies, ubiquitous computing and social networks.
\end{statement}

\section{Key Achievements}

\achievements
{Optimized product adoption by designing and implementing a \href{http://developers.sensetecnic.com/}{Developer Hub} which included API documentation, libraries and development guides.}
{Created a novel web framework (\href{http://red.calderonroberto.com}{RED}) to allow developers 
to prototype and deploy applications spanning multiple displays, sensors, actuators and wearable devices.}
{Founded several business ventures in the technology and design industries.}
{}

\section{Work}

% \workitem
% {}%Company
% {}%Years 
% {}%Title 
% {}%Dates
% {}%Responsibilities
% {}%Achievement(1)
% {}%Achievement(2) %optional
% {}%Achievement(3) %optional

\workitem{\href{http://sensetecnic.com}{SenseTecnic Systems Inc.}}%Company
{2015--present}%Dates
{Software Developer and Evangelist.} %Title 
{This role involved a combination of software developer, product evangelist and customer liaison responsibilities.}%Responsibilities
% Achievement
{Created and maintained developer libraries and guides (\href{http://developers.sensetecnic.com}{developers.sensetecnic.com}) to access our REST API and advocated their use among developer communities}
{Developed and demonstrated example IoT (Internet of Things) applications to existing and prospective clients in order to grow business}
{Designed, developed and tested beta back-end and front-end product features using NodeJS, Python, Ruby, HTML5, CSS/LESS and Javascript}
{}
{}

\workitem{\href{http://research.magic.ubc.ca/}{Media and Graphics Interdisciplinary Centre at UBC}}%Company
{2010--2014}%Dates
{Software Developer -- Graduate Research Assistant.} %Title
{In charge of developing and evaluating web technologies and applications, conducting HCI research and supervising co-op student teams.} %Responsibilities
% Achievements
{Created and exercised a novel web framework (\href{http://red.calderonroberto.com}{http://red.calderonroberto.com}) to easily prototype ubiquitous computing applications  using Javascript, HTML5, CSS/SASS, RoR, Python and Java}
{Conducted HCI research including gathering user requirements, conducting usability studies, and performing statistical evaluation of medium and high fidelity applications}
{Managed teams of co-op student developers by outlining project requirements, mentoring students and ensuring results were delivered on target}
{}
{}

\workitem{\href{http://isgp.ubc.ca/}{Interdisciplinary Studies Graduate Department at UBC}}
{2009--2014}
{DevOps, Web Developer and Advocate -- Graduate Research Assistant.} %Title
{This role involved development, operation and maintenance of the department's web site and social media strategy.}
% Achievements
{Led the re-design and migration of the department's legacy website to WordPress, implementing several custom-built PHP modules}
{Applied User Experience and Search Engine Optimization practices to improve the web site's usability and online presence}
{}
{}

\workitem{\href{http://box60.calderonroberto.com}{Box 60 Inc.}}
{2011--2012}
{Co-Founder -- CTO} %Title
{I ensured that the company's technology strategy served its business goal by leading the design and implementation of our product.} %Responsibilities
% Achievements
{Created a company connecting mobile applications to Restaurant Point of Sales (PoS) for highly personalized dining experiences}
{Designed, developed and real-world tested a scalable SaaS service using Java, RoR and HTM5}
{Led a team of software developers, using agile practices, into producing a minimum viable product under a very tight budget and short timeline}
{}
{}

% \workitem{\href{http://www.uaemex.mx/}{Universidad Autonoma del Estado de Mexico.}}
% {2005--2007}
% {Sessional Lecturer} %Title
% {Teaching \emph{Three-Dimensional Digital Design} and \emph{Semiotics and Poetry} in the Faculty of Architecture and Design.} %Responsibilities
% % Achievements
% {Initiated and coordinated a redevelopment of the curriculum to include experimental research in computer-based architectural practice}
% {Led studio research projects focusing on real world applications and social impact of architectural design}
% {}
% {}
% {}

\workitem{\href{http://www.omgarq.com/}{OMG ARQ}}
{2001--2006}
{Architect} %Title
{In charge of conception, design and construction of residential projects through architectural designs, digital renderings and technical documentation for building contractors.} %Responsibilities
% Achievements
{Project manager for the design and construction of multiple residences, ensuring they were delivered on time and within budget}
{Managed multiple teams of designers, building contractors, lawyers and architects, and coordinated project operations}
{}
{}
{}

\workitem{\href{http://www.mimesisarquitectura.com/}{Mimesis Arquitectura}}
{2002--2005}
{Co-Founder} %Title
{Built an architecture firm seeking to bring diverse fields of study into architecture practice through multidisciplinary research.} %Responsibilities
% Achievements
{Grew a successful and profitable business while studying a highly demanding degree in Architecture, Industrial and Product Design}
{Implemented development practices from the field of software engineering (scrum and extreme programming) to improve and optimize architectural design practices}
{}
{}
{}

\section{Education}

\datedsubsection{University of British Columbia}{2009--Present}
Ph.D. Human Computer Interaction (HCI).
\datedsubsection{University of British Columbia}{2007--2009}
M.Sc. Interdisciplinary Studies, HCI Specialization.
\datedsubsection{Universidad Iberoamericana}{1999--2005}
Bachelor of Architecture, Industrial and Product Design

\begin{riddle}
\ghost
\end{riddle}

\end{document} ​
